TBD

### 2021-02-26 outputs/paper/paper.Rmd
Just removed a needless heading in results section.
Altered graph groupings

In terms of effects on revenue and/or overall sales for restaurants during the intervention period, Figure \@ref(fig:reveffects) shows us that more restaurants within the treatment group saw decreases in revenue compared to the prior quarter (July 1 - Sep 30), while the control group's revenue largely remained the same. In addition to this, it shows that of those restaurants that saw a decrease in revenue, the treatment group saw the harshest declines in revenue during the intervention period. A Chi-Square test for whether the restaurant saw a decrease in revenue showed that restaurants in the treatment group were more likely to report a decrease in revenue *X*^2^ (2, *N* = 330) = 220.73, *p* < 2.2e-16. The percentage decrease in revenues also showed a significant relationship, where restaurants in the treatment group are most likely to report higher loss of revenue during the intervention period *X*^2^ (3, *N* = 330) = 178.33, *p* < 2.2e-16. Prior to the intervention period, it appears as though both groups had similar breakdowns of revenue coming from take-out and/or delivery (Figure 7).

### Effects of Intervention on Revenue

@@

Questions related to the adjustments of the restaurants during the intervention, such as a menu price, and hours and days of operation (Figure \@ref(fig:opseffects)) show us that:

@@

```{r Q11, echo = FALSE, message = FALSE}
### Between (start date of intervention) and (end date of intervention), did you make any adjustments to your menu prices?
### Yes, prices were raised
### Yes, prices were lowered
### No changes were made
q11 <- ggplot(data = all_simulated_dataset, mapping = aes (x = Q10, fill = type)) +
  geom_bar() +  
  coord_flip() + 
  scale_x_discrete(limit = c("Yes, prices were raised", "Yes, prices were lowered", "No changes were made")) + 
  labs(x = "Adjustments to Menu Prices",
       y = "# of Restaurants",
       title = str_wrap("Menu adjustments between Oct 1 and Dec 31", 30),
       fill = "Condition") +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme_fivethirtyeight()

@@

```{r Q12, echo = FALSE, message = FALSE}
### Between (start date of intervention) and (end date of intervention) did you reduce your ### restaurant’s hours of operation?
### Yes
### No
q12 <- ggplot(data = all_simulated_dataset, mapping = aes(x = Q12, fill = type)) +
  geom_bar(position = position_dodge(1)) +
  labs(x = "Reduction in hours of operation",
       y = "# of restaurants",
       title = str_wrap("Reducton in operating hours between Oct 1 and Dec 31", 30),
       fill = "Condition") +
  theme_fivethirtyeight() +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))

@@

@@

```{r opseffects, fig.width=11.5, fig.height=10, echo = FALSE, message = FALSE, fig.cap="Effects on hours and days of operation as a result of intervention by condition"}
grid.arrange(q11, q12, q13, q14, q15)
```

>>>>

In terms of effects on revenue and/or overall sales for restaurants during the intervention period, Figure \@ref(fig:reveffects) shows us that more restaurants within the treatment group saw decreases in revenue compared to the prior quarter (July 1 - Sep 30), while the control group's revenue largely remained the same. In addition to this, it shows that of those restaurants that saw a decrease in revenue, the treatment group saw the harshest declines in revenue during the intervention period. A Chi-Square test for whether the restaurant saw a decrease in revenue showed that restaurants in the treatment group were more likely to report a decrease in revenue *X*^2^ (2, *N* = 330) = 220.73, *p* < 2.2e-16. The percentage decrease in revenues also showed a significant relationship, where restaurants in the treatment group are most likely to report higher loss of revenue during the intervention period *X*^2^ (3, *N* = 330) = 178.33, *p* < 2.2e-16. Prior to the intervention period, it appears as though both groups had similar breakdowns of revenue coming from take-out and/or delivery.

@@

Questions related to the adjustments of the restaurants during the intervention, such as a menu price, and hours and days of operation (Figures \@ref(fig:Q11), \@ref(fig:opshourseffects), and \@ref(fig:opsdayseffects)) show us that:

@@

```{r Q11, fig.height = 2.5, fig.width = 6, echo = FALSE, message = FALSE, fig.cap = "Menu adjustments during the intervention period (Oct 1 - Dec 31)"}
### Between (start date of intervention) and (end date of intervention), did you make any adjustments to your menu prices?
### Yes, prices were raised
### Yes, prices were lowered
### No changes were made
ggplot(data = all_simulated_dataset, mapping = aes (x = Q10, fill = type)) +
  geom_bar() +  
  coord_flip() + 
  scale_x_discrete(limit = c("Yes, prices were raised", "Yes, prices were lowered", "No changes were made")) + 
  labs(x = "Adjustments to Menu Prices",
       y = "# of Restaurants",
       title = str_wrap("Menu adjustments between Oct 1 and Dec 31", 30),
       fill = "Condition") +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme_fivethirtyeight()

@@

```{r Q12, echo = FALSE, message = FALSE}
### Between (start date of intervention) and (end date of intervention) did you reduce your ### restaurant’s hours of operation?
### Yes
### No
q12 <- ggplot(data = all_simulated_dataset, mapping = aes(x = Q12, fill = type)) +
  geom_bar(position = position_dodge(1)) +
  labs(x = "Reduction in hours of operation",
       y = "# of restaurants",
       title = str_wrap("Reduction in operating hours between Oct 1 and Dec 31", 30),
       fill = "Condition") +
  theme_fivethirtyeight() +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))

@@

```{r opshourseffects, fig.width = 5, fig.height = 4.8, echo = FALSE, message = FALSE, fig.cap="Effects on hours and days of operation as a result of intervention by condition"}
grid.arrange(q12, q13)
```

@@

```{r opsdayseffects, fig.width = 6, fig.height = 4.8, echo = FALSE, message = FALSE, fig.cap="Effects on hours and days of operation as a result of intervention by condition"}
grid.arrange(q14, q15)
```
